The World Bank, Women, Business and the Law

### 2024-04-23 outputs/paper/paper.qmd

---
title: "The World Bank, Women, Business and the Law"
subtitle: "How Canada's working women fare in the business world"
author: 
  - Sehar Bajwa
  - Luca Carnegie
thanks: "Code and data are available at: https://github.com/lcarnegie/replicationpaper. "
date: February 20, 2024
date-format: long
abstract: "Gender-based legal frameworks and workplace conditions are crucial considerations in the pursuit of global gender equality. This paper replicates and extends the data analysis conducted by Hyland et al. on the World Bank's 'Women, Business, and the Law' dataset.  By cross-referencing the World Bank's indicators with Statistics Canada's data, we delve into the nuanced realities of gender-related legal frameworks and business regulations. The revelations underscore the need for a comprehensive and more practical approach in evaluating gender inclusivity within legal and business domains. "
format: pdf
number-sections: true
bibliography: references.bib
toc: true
---

>>>>

---
title: "The World Bank, Women, Business and the Law"
subtitle: "How Canada's working women fare in the business world"
author: 
  - Sehar Bajwa
  - Luca Carnegie
thanks: "Code and data are available at: https://github.com/lcarnegie/replicationpaper. "
date: February 20, 2024
date-format: long
abstract: "Understanding gender-based differences in legal frameworks and workplace conditions is important in the pursuit of global gender equality. This paper replicates and extends Hyland, ASDFA, ASDFASF (). We examine gender-related legal frameworks and business regulations globally, and then compare the World Bank's indicators with those of Statistics Canada to focus on Canada. We find that nuances in country-level datasets are important for understanding the biases faced by women in different countries, which underscores the difficulty of constructing cross-country datasets."
format: pdf
number-sections: true
bibliography: references.bib
toc: true
---
